Multi sky-view\\ 3D aerosol distribution recovery

### 2013-07-31 article.tex
Fixed results image.

A set of ground-based wide-angle cameras
looks upwards (\cref{fig:groundgrid}), performing {\em
  integral imaging}~\cite{Hong2004} of the sky. Per viewpoint, the
view azimuth and elevation angles (relative to the zenith and north)
are encapsulated in vector ${\bm{\Theta}}$. Any camera $c$ is at a
distinct fixed location, capturing raw image
$i_c({\bm{\Theta}})$. This paper takes a first step of formulating
a principle for estimating the 3D atmospheric aerosols distribution,
using such data. To study the feasibility and cross validate it, we perform RT
using two different forward models. A forward model takes as input a 3D aerosol distribution, and outputs images as if captured at various viewpoints. 
One model uses MC (\cref{sec:monte-carlo-simul}): it is stochastic,
slow but naturally expresses multiple-scattering. Hence, MC
rigorously simulates realistic scenes of arbitrary complexity. 
%MC simulations can be made arbitrarily accurate by increasing the number of launched %photons. MC methods are highly parallelizable. 
The second model uses the single-scattering approximation
(\cref{sec:single-scatt-model}). It is less accurate than MC, but
solves RT in an analytic, closed form. This form
enables simple inversion of the model, to estimate the underlying
aerosol distribution (\cref{sec:inverse-problem}).

@@

The MC simulations rely on the same grid as Sec.~\ref{sec:single-scatt-model}. We use backward MC: from a detector pixel, photons are `launched' via the camera lens; then the photons are traced back through the atmosphere. Photons that happen to be back-traced to the Sun are counted, per pixel. In this model, RT takes the following steps, per launched photon (\cref{fig:mcgrid}):\\
({\tt i}) Launch a photon from camera $c$ to direction ${\bm{\Theta}}$. This is the initial {\em ray}, denoted ${\cal R}_0$.\\
Per iteration $i$\\
({\tt ii}) Find the distance on ray ${\cal R}_{i}$ to which the photon propagates. To do this, Eq.~(\ref{eq:taurand}) yields $\tau^{\rm random}$. Then, Eq.~(\ref{eq:lrand}) generalizes to a non-uniform atmosphere: using Eq.~(\ref{eq:tau}), numerically seek $l^{\rm random}$ s.t.
\begin{align}
  \int_0^{l^{\rm random}}(\sigma^{\rm aerosol} n +\beta^{\rm air}) dl = \tau^{\rm random}
  \label{eq:MCextinct}
\end{align}
Distance $l^{\rm random}$ at ${\cal R}_{i}$ is 3D position ${\bf X}_{i}$.
If  ${\bf X}_{i}$ is outside the atmospheric grid, the photon is terminated. If, in addition,  ${\cal R}_{i}\parallel {\rm SR}$ , the photon is counted as contributing to the image pixel.\\
({\tt iii}) The type of particle (air molecule or aerosol) the photon interacts with at ${\bf X}_{i}$ is determined randomly according to their relative densities at the voxel containing ${\bf X}_{i}$.\\
({\tt iv}) If it is an aerosol, the photon is terminated with probability 
$1-\varpi^{\rm aerosol}$.\\
({\tt v}) The photon is scattered to a new direction, determined by inverse transform sampling, according to the phase function of the particle: \cref{eq:aerosol_scatter}
or~\cref{eq:rayleighP}. This yields a new {\em ray}, denoted ${\cal R}_{i+1}$, emanating from ${\bf X}_{i}$. The next iteration of propagation (denoted {\tt ii} above)  proceeds.\\
Local Estimation~\cite{marshak20053d} is used for calculating the amount of light back-traced to the sun at each scattering.

@@

An iso-surface visualization of the original {\em Haze Blobs}
distribution is shown in \cref{fig:results}a. \cref{fig:results}c show
the reconstructed scene based on images simulated by the Single
Scattering model. \cref{fig:results}e visualizes the reconstructed
scene based on images simulated by the MC model. The distributions
appear consistent, though there are errors that stem from the random
noise in the images. To quantify the results, we use a relative error
measure based on the $\ell_1$ norm
\begin{equation}
  \label{eq:ndiff}
  \epsilon=\frac{\| \hat{\bm n}  - {\bm n}^{\rm true} \|_1}
  {\| {\bm n}^{\rm true} \|_1} ,
\end{equation}
It is equivalent to the aerosol mass that is over and under-estimated
in all voxels, relative to the total aerosol mass in the scene.  In
the {\em Haze Blobs} case, $\epsilon=0.571$ and $\epsilon=0.72$ for
the reconstructions based on the Single-Scattering images and MC
images respectively. We used the distribution reconstructed based on
the MC images to create images using the Single-Scattering
model. \cref{fig:simulation-results1}c shows a cross of such an image
compared to the original MC image.

We created a {\em Haze Front} scene. \cref{fig:results}b shows an
iso-surface visualization of this distribution.
\begin{figure}
  \centering
  \yoavcomment{\includegraphics[width=\columnwidth]{images/results}}
  \caption{\small [a] and [b] Simulated 3D aerosol distribution
    composed of a {\em Haze Front} and {\em Haze Front}
    respectively. [c] and [d] Reconstruction of the same scenes when
    using Single-Scattering simulated images as input.  [e] and [f]
    Reconstruction of the scenes when using MC simulated images as
    input.  Color represents aerosol density. The density units are
    $10^{6}~{\rm particles}/{\rm m}^3.$}
  \label{fig:results}
\end{figure}
Here an ellipsoid degenerated to an elliptic cylinder that partly
enters the analyzed volume. It is centered at altitude \SI{5}{\km},
has vertical thickness of \SI{4}{\km} and length of \SI{32}{\km} (only
part of which enters the volume). The haze front stretches across the
width of the volume.  \cref{fig:results}d and \cref{fig:results}f
visualizes the recovered 3D distribution of this scene. For the {\em
  Haze Front}, $\epsilon=0.46$ and $\epsilon=0.62$ for the
reconstructions based on the Single-Scattering images and MC images
respectively.

>>>>

A set of ground-based wide-angle cameras looks upwards
(\cref{fig:groundgrid}), performing {\em integral
  imaging}~\cite{Hong2004} of the sky. Per viewpoint, the view azimuth
and elevation angles (relative to the zenith and north) are
encapsulated in vector ${\bm{\Theta}}$. Any camera $c$ is at a
distinct fixed location, capturing raw image
$i_c({\bm{\Theta}})$. This paper takes a first step of formulating a
principle for estimating the 3D atmospheric aerosols distribution,
using such data. To study the feasibility and cross validate it, we
perform RT using two different forward models. A forward model takes
as input a 3D aerosol distribution, and outputs images as if captured
at various viewpoints.  One model uses MC
(\cref{sec:monte-carlo-simul}): it is stochastic, slow but naturally
expresses multiple-scattering. Hence, MC rigorously simulates
realistic scenes of arbitrary complexity.
% MC simulations can be made arbitrarily accurate by increasing the
% number of launched %photons. MC methods are highly parallelizable.
The second model uses the single-scattering approximation
(\cref{sec:single-scatt-model}). It is less accurate than MC, but
solves RT in an analytic, closed form. This form enables simple
inversion of the model, to estimate the underlying aerosol
distribution (\cref{sec:inverse-problem}).

@@

The MC simulations rely on the same grid as
Sec.~\ref{sec:single-scatt-model}. We use backward MC: from a detector
pixel, photons are `launched' via the camera lens; then the photons
are traced back through the atmosphere. Photons that happen to be
back-traced to the Sun are counted, per pixel. In this model, RT takes
the following steps, per launched photon (\cref{fig:mcgrid}):

\noindent ({\tt i}) Launch a photon from camera $c$ to direction
${\bm{\Theta}}$. This is the initial {\em ray}, denoted ${\cal R}_0$.

\noindent Per iteration $i$

\noindent ({\tt ii}) Find the distance on ray ${\cal R}_{i}$ to which the photon
propagates. To do this, Eq.~(\ref{eq:taurand}) yields $\tau^{\rm
  random}$. Then, Eq.~(\ref{eq:lrand}) generalizes to a non-uniform
atmosphere: using Eq.~(\ref{eq:tau}), numerically seek $l^{\rm
  random}$ s.t.
\begin{align}
  \int_0^{l^{\rm random}}(\sigma^{\rm aerosol} n +\beta^{\rm air}) dl
  = \tau^{\rm random}
  \label{eq:MCextinct}
\end{align}
Distance $l^{\rm random}$ at ${\cal R}_{i}$ is 3D position ${\bf
  X}_{i}$.  If ${\bf X}_{i}$ is outside the atmospheric grid, the
photon is terminated. If, in addition, ${\cal R}_{i}\parallel {\rm
  SR}$ , the photon is counted as contributing to the image pixel.

\noindent ({\tt iii}) The type of particle (air molecule or aerosol) the photon
interacts with at ${\bf X}_{i}$ is determined randomly according to
their relative densities at the voxel containing ${\bf X}_{i}$.

\noindent ({\tt iv}) If it is an aerosol, the photon is terminated with
probability $1-\varpi^{\rm aerosol}$.

\noindent ({\tt v}) The photon is scattered to a new direction, determined by
inverse transform sampling, according to the phase function of the
particle: \cref{eq:aerosol_scatter} or~\cref{eq:rayleighP}. This
yields a new {\em ray}, denoted ${\cal R}_{i+1}$, emanating from ${\bf
  X}_{i}$. The next iteration of propagation (denoted {\tt ii} above)
proceeds.

\noindent Local Estimation~\cite{marshak20053d} is used for calculating the
amount of light back-traced to the sun at each scattering.

@@

An iso-surface visualization of the original {\em Haze Blobs}
distribution is shown in \cref{fig:results}a. \cref{fig:results}c show
the reconstructed scene based on images simulated by the Single
Scattering model. \cref{fig:results}e visualizes the reconstructed
scene based on images simulated by the MC model. The distributions
appear consistent, though there are errors that stem from the random
noise in the images. To quantify the results, we use a relative error
measure based on the $\ell_1$ norm
\begin{equation}
  \label{eq:ndiff}
  \epsilon=\frac{\| \hat{\bm n}  - {\bm n}^{\rm true} \|_1}
  {\| {\bm n}^{\rm true} \|_1} ,
\end{equation}
It is equivalent to the aerosol mass that is over and under-estimated
in all voxels, relative to the total aerosol mass in the scene.  In
the {\em Haze Blobs} case, $\epsilon=0.143$ and $\epsilon=0.646$ for
the reconstructions based on the Single-Scattering images and MC
images respectively. We used the distribution reconstructed based on
the MC images to create images using the Single-Scattering
model. \cref{fig:simulation-results1}c shows a cross of such an image
compared to the original MC image.

We created a {\em Haze Front} scene. \cref{fig:results}b shows an
iso-surface visualization of this distribution.
\begin{figure}
  \centering
  \yoavcomment{\includegraphics[width=\columnwidth]{images/results}}
  \caption{\small [a] and [b] Simulated 3D aerosol distribution
    composed of a {\em Haze Front} and {\em Haze Front}
    respectively. [c] and [d] Reconstruction of the same scenes when
    using Single-Scattering simulated images as input.  [e] and [f]
    Reconstruction of the scenes when using MC simulated images as
    input.  Color represents aerosol density. The density units are
    $10^{6}~{\rm particles}/{\rm m}^3.$}
  \label{fig:results}
\end{figure}
Here an ellipsoid degenerated to an elliptic cylinder that partly
enters the analyzed volume. It is centered at altitude \SI{5}{\km},
has vertical thickness of \SI{4}{\km} and length of \SI{32}{\km} (only
part of which enters the volume). The haze front stretches across the
width of the volume.  \cref{fig:results}d and \cref{fig:results}f
visualizes the recovered 3D distribution of this scene. For the {\em
  Haze Front}, $\epsilon=0.199$ and $\epsilon=0.654$ for the
reconstructions based on the Single-Scattering images and MC images
respectively.
